Potential impact of seasonal forcing on a SARS-CoV-2 pandemic

### 2020-03-11 manuscript/main.tex
make composite figures

\begin{figure*}
    \centering
    \includegraphics[width=\columnwidth]{figures/pos_frac_vs_time.pdf}
    \includegraphics[width=\columnwidth]{figures/pos_frac_by_month.pdf}
    \caption{{\bf Seasonal variation in the fraction of positive CoV tests in Stockholm, Sweden.} The left panel shows test results between 2010 and 2019. The right panel shows aggregated data for all years. All CoVs show a marked decline in summer and autumn, with HKU1/OC43 peaking January--December, and NL63 and 229E peaking in February--March. %\Emma{(OK? Seemed a very short fig description.} \Jan{Yes, good. Added a little about the two panels}
    }
    \label{fig:seasonal_CoV}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/fit_2.3.pdf}
    \caption{{\bf Compatibility of SEIR model trajectories with observations.} The heatmap shows the inverse mean squared deviation between the model trajectories and the observed seasonal forcing in seasonal CoV prevalence. Model and observations are compatible (yellow shading) in a region of parameter values corresponding to low migration/weak seasonality and second region at high migration/strong seasonality. Migration refers to the rate per year of a susceptible to return from a abroad with a CoV infection.}
    \label{fig:parameter_seasonal}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\columnwidth]{figures/scenarios.pdf}
    \includegraphics[width=\columnwidth]{figures/peak_ratio_0.5.pdf}
\caption{{\bf Model predictions for SARS-CoV-2 case numbers in temperate zones for a pandemic scenario}. The left panel shows example trajectories assuming SARS-CoV-2 transmissibility peaks in November, January, or March. 
These outbreaks in Northern Europe (`NE') are assumed to be seeded by the outbreak in Hubei (model trajectory shown as a dashed line).
Within the model, these cases are exported at rate of 0.01/year to temperate Northern Europe with an average $\langle R_0\rangle = 2.2$ and seasonal forcing of $\forcing=0.5$. Corresponding graphs for different values of $\langle R_0\rangle$ and the migration rate are shown in Supplemental Fig.~S\ref{fig:scenarios_supp}.
The right panel shows the ratio of the first and second peak for a range of different combinations of $R_0$ and $\theta$. 
The yellow area corresponds to parameter combinations with essentially only an early peak similar to the yellow line on the left. 
The blue/purple area shows parameter combinations for which a peak in late 2020 dominates, as with the purple line on the left, while the central pink/orange band shows the combinations giving rise to two comparable peaks. 
These simulations are for $\forcing=0.5$. Similar results were obtained for $\forcing=0.3$ and 0.7, see Supplementary  Fig.~\ref{fig:peak_ratio_supp}.}
    \label{fig:nCov_predictions}
\end{figure*}

@@

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/global_3_panel_2.2.pdf}
    \caption{{\bf Extended circulation through overlapping epidemics in variable subpopulations.} These simulations of a pandemic scenario assume 1,000 sub-populations with an average $\langle R_0\rangle$ of 2.2 and standard deviation $0.5$, 40\% of which have weak seasonal forcing $\forcing \in [0,0.2]$ (tropical) and the remainder have strong variation with $\forcing \in [0.25,0.75]$. The super-position of many variable epidemics can result in a global prevalence that decays only slowly through 2020 and 2021. 
    Lighter lines have lower $R_0$, darker lines have higher $R_0$. 
    The actual observed case counts reported for Hubei are added (brown line) and multiplied by three to account for possible under-reporting of mild cases. A subset of 30 randomly chosen simulations are plotted for each region.
    Analogous figures for different $R_0$ parameter values are shown in Supplementary Fig.~\ref{fig:global_3_panel_supp}.}
    \label{fig:global_3_panel}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/global_endemic_2.2.pdf}
    \caption{{\bf Transition to an endemic seasonal virus.} 
    If previously infected individuals can be reinfected after some time, as for example by seasonal influenza virus, SARS-CoV-2 could develop into a seasonal CoV that returns every winter. This would typically happen at much lower prevalence than peak pandemic levels. 
    These simulations assume reinfection on average every 10 years.}
    \label{fig:endemic}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/fig_1.pdf}
    % \includegraphics[width=\columnwidth]{figures/pos_frac_vs_time.pdf}
    % \includegraphics[width=\columnwidth]{figures/pos_frac_by_month.pdf}
    \caption{{\bf Seasonal variation in the fraction of positive CoV tests in Stockholm, Sweden.} Panel A shows test results between 2010 and 2019. Panel B shows aggregated data for all years. All CoVs show a marked decline in summer and autumn, with HKU1/OC43 peaking January--December, and NL63 and 229E peaking in February--March. %\Emma{(OK? Seemed a very short fig description.} \Jan{Yes, good. Added a little about the two panels}
    }
    \label{fig:seasonal_CoV}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/fig_2.pdf}
    % \includegraphics[width=\columnwidth]{figures/fit_2.3.pdf}
    \caption{{\bf Compatibility of SEIR model trajectories with observations.} The heatmap shows the inverse mean squared deviation between the model trajectories and the observed seasonal forcing in seasonal CoV prevalence. Model and observations are compatible (yellow shading) in a region of parameter values corresponding to low migration/weak seasonality and second region at high migration/strong seasonality. Migration refers to the rate per year of a susceptible to return from a abroad with a CoV infection.}
    \label{fig:parameter_seasonal}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/fig_3.pdf}
    % \includegraphics[width=\columnwidth]{figures/scenarios.pdf}
    % \includegraphics[width=\columnwidth]{figures/peak_ratio_0.5.pdf}
\caption{{\bf Model predictions for SARS-CoV-2 case numbers in temperate zones for a pandemic scenario}. Panel A shows example trajectories assuming SARS-CoV-2 transmissibility peaks in November, January, or March.
These outbreaks in Northern Europe (`NE') are assumed to be seeded by the outbreak in Hubei (model trajectory shown as a dashed line).
Within the model, these cases are exported at rate of 0.01/year to temperate Northern Europe with an average $\langle R_0\rangle = 2.2$ and seasonal forcing of $\forcing=0.5$. Corresponding graphs for different values of $\langle R_0\rangle$ and the migration rate are shown in Supplemental Fig.~S\ref{fig:scenarios_supp}.
Panel B shows the ratio of the first and second peak for a range of different combinations of $R_0$ and $\theta$.
The yellow area corresponds to parameter combinations with essentially only an early peak similar to the yellow line on the left.
The blue/purple area shows parameter combinations for which a peak in late 2020 dominates, as with the purple line on the left, while the central pink/orange band shows the combinations giving rise to two comparable peaks.
These simulations are for $\forcing=0.5$. Similar results were obtained for $\forcing=0.3$ and 0.7, see Supplementary  Fig.~\ref{fig:peak_ratio_supp}.}
    \label{fig:nCov_predictions}
\end{figure*}

@@

\begin{figure*}[tb]
    \centering
    % \includegraphics[width=\textwidth]{figures/global_3_panel_2.2.pdf}
    \includegraphics[width=\textwidth]{figures/fig_4.pdf}
    \caption{{\bf Extended circulation through overlapping epidemics in variable subpopulations.} These simulations of a pandemic scenario assume 1,000 sub-populations with an average $\langle R_0\rangle$ of 2.2 and standard deviation $0.5$, 40\% of which have weak seasonal forcing $\forcing \in [0,0.2]$ (tropical) and the remainder have strong variation with $\forcing \in [0.25,0.75]$. The super-position of many variable epidemics can result in a global prevalence that decays only slowly through 2020 and 2021.
    Lighter lines have lower $R_0$, darker lines have higher $R_0$.
    The actual observed case counts reported for Hubei are added (brown line) and multiplied by three to account for possible under-reporting of mild cases. A subset of 30 randomly chosen simulations are plotted for each region.
    Analogous figures for different $R_0$ parameter values are shown in Supplementary Fig.~\ref{fig:global_3_panel_supp}.}
    \label{fig:global_3_panel}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/fig_5.pdf}
    % \includegraphics[width=\columnwidth]{figures/global_endemic_2.2.pdf}
    \caption{{\bf Transition to an endemic seasonal virus.}
    If previously infected individuals can be reinfected after some time, as for example by seasonal influenza virus, SARS-CoV-2 could develop into a seasonal CoV that returns every winter. This would typically happen at much lower prevalence than peak pandemic levels.
    These simulations assume reinfection on average every 10 years.}
    \label{fig:endemic}
\end{figure}
